The Role of Context in Spatial Region Identification

### 2013-11-13 scenarios/cdsr/trunk/papers/ACS2013/main.tex

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
\begin{tabular}{c c c} 
  \begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom.png}
%  \caption{``The front of the classroom'' could be defined as the area between the desks and the whiteboard where people give presentations.}
  \caption{``The front of the classroom''.}
  \end{subfigure} &
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/safety-3.jpg}
%  \caption{Safety for the scout is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
  \caption{``The safe region for the scout''.}
\end{subfigure} & 
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck.JPG}
%  \caption{A bottleneck occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
 \caption{``The bottleneck''.}
  \label{fig:safety}
  \end{subfigure}\\
\end{tabular}
  \caption{Examples of spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}

Understanding CDSRs is crucial to joint intelligent action with humans; among other reasons they are frequently tieds to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety''. In the rest of the paper we present a study that examines the contextual dependence of these regions.  Following this we discuss how the results align with previous research and requirements for a cognitive systems model of this ability.

@@

>>>>

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
\begin{tabular}{c c c} 
  \begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom-label.png}
%  \caption{``The front of the classroom'' could be defined as the area between the desks and the whiteboard where people give presentations.}
  \caption{``The front of the classroom''.}
  \end{subfigure} &
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/tanks-close-label.jpg}
%  \caption{Safety for the scout is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
  \caption{``The safe region for the scout''.}
\end{subfigure} & 
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck-label.JPG}
%  \caption{A bottleneck occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
 \caption{``The bottleneck''.}
  \label{fig:safety}
  \end{subfigure}\\
\end{tabular}
  \caption{Examples of the spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}

Understanding CDSRs is crucial to joint intelligent action with humans; among other reasons they are frequently tieds to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety''.  We claim that (1) people can effectively communicate using these regions and (2) the size, location and shape of these regions change with the context.  To explore these claims, we present the results of a human study in which people marked regions and rated points representing CDSRs in three different environments in 13 different contexts.  In discussing the results, we consider the applicability of approaches from cognitive systems and robotics.  We posit that to account for this ability, a cognitive system must respond to changing context, apply learned regions to new contexts, and reuse learned knowledge in multiple tasks.  Current approaches have a number of shortcomings that must be addressed not only to improve our understanding of human spatial reasoning, but also to enable robust intelligent assistants in human environments.

@@

\subsection{discussion}
Taken together, these results support the following conclusions. First, people are able to agree on location and area of CDSRs.  This agreement is reduced in situations where the domain knowledge of the context is ambiguous, such as, the circular desk arrangement or the defensive capabilities of a single turret.  Second, changing the context predictably changes the subjects assessments of location, shape and size of the CDSR.  These results were supported by tasks involving people labeling regions as well as rating individual points.  On the other hand, our experiments produced mixed results concerning our hypothesis that people use simulation to evaluate dynamic changes to CDSRs.  Further studies are required to control for the domain knowledge of the participants exploring this question.
